Towards Transparency and Open Science

### 2023-02-19 manuscript.Rmd

I used several digital aids to improve the writing (not the content), including grammerly.com, deepl.com, and mentor.duden.de.
Also, to aid with the clarity of the writing, I asked Andreas Brandmaier, Carli Ochs, Leo Richter, Leonie Haggitte, and Caroline Gahrmann for feedback.
Furthermore, I asked Leo Richter and Maximilian Ernst for help with mathematical notation and typesetting.
Julia Delius has kindly agreed to proofread the journal articles at the time of submission and the synopsis of the thesis.
All the errors that remain are solely my responsibility.
[I also prompted `ChatGPT` to write a song about reproducibility; while it was amusing, it was not funny enough to make an appearance in the text](https://github.com/aaronpeikert/repro-talk/blob/master/gpt-songs.md).

@@

<!--necessity of induction-->
In other words, induction gives theories some leeway to be imprecise and contain "blank" spaces, filled in later based on observation.
It allows researchers to focus on the essential statements of their theories and choose to leave some parts (such as auxiliary assumptions) to be determined inductively.
In some ways, it is the empirical researchers' answer to the Duhem–Quine problem [@duhemPhysicalTheoryExperiment1976; @vanormanquineTwoDogmasEmpiricism1976], which states that any empirical test of a theory is testing the conjunction of theory, auxiliary assumptions, and conjectures [@meehlTheoreticalRisksTabular1978; @meehlAppraisingAmendingTheories1990].
Auxiliary assumptions are necessary to test a theory but do not follow from the theory itself.
If such assumptions do not hold, they may lead to empirical falsification even though the theory holds.
However, if an auxiliary assumption is induced, it can not be falsified by the same data that induced it.
Inducing such assumptions, therefore, effectively removes auxiliary assumptions from the conjunction that is exposed to falsification.
Since empirical researchers cannot always derive every assumption from their theory, avoiding refutation because of those assumptions is a desirable property.

<!--statistical induction can be dangerous-->
By the same token, entire theories may escape refutation by replacing every ill-fitting statement deduced from theory with statements induced from data.
If applied to auxiliary assumptions, such a strategy of changing a theory post hoc in light of facts has been called "Lakatosian Defense" [@meehlAppraisingAmendingTheories1990].
If pushed to the limit, we arrive at a "theory" governed by the data.
Such a theory, full of empirically induced statements, is almost empty of statements that have been empirically verified.
The data used for induction can not refute these statements, so they have never been subjected to an empirical test.

>>>>

I used several digital aids to improve the writing (not the content), including grammerly.com, deepl.com, and mentor.duden.de.
Also, to aid with the clarity of the writing, I asked Andreas Brandmaier, Carli Ochs, Leo Richter, Leonie Hagitte, and Caroline Gahrmann for feedback.
Furthermore, I asked Leo Richter and Maximilian Ernst for help with mathematical notation and typesetting.
Julia Delius has kindly agreed to proofread the journal articles at the time of submission and the synopsis of the thesis.
All the errors that remain are solely my responsibility.
[I also prompted `ChatGPT` to write a song about reproducibility; while it was amusing, it was not funny enough to make an appearance in the text](https://github.com/aaronpeikert/repro-talk/blob/master/gpt-songs.md).

@@

<!--necessity of induction-->
In other words, induction gives theories some leeway to be imprecise and contain "blank" spaces, filled in later based on observation.
It allows researchers to focus on the essential statements of their theories and choose to leave some parts (such as auxiliary assumptions) to be determined inductively.
In some ways, it is the empirical researchers' answer to the Duhem–Quine problem [@duhemPhysicalTheoryExperiment1976; @vanormanquineTwoDogmasEmpiricism1976], which states that any empirical test of a theory is testing the conjunction of theory, auxiliary assumptions, and conjectures [@meehlTheoreticalRisksTabular1978; @meehlAppraisingAmendingTheories1990].
Auxiliary assumptions are necessary to test a theory but do not follow from the theory itself.
If such assumptions do not hold, they may lead to empirical falsification even though the theory holds.
However, if an auxiliary assumption is induced, it cannot be falsified by the same data that induced it.
Inducing such assumptions, therefore, effectively removes auxiliary assumptions from the conjunction that is exposed to falsification.
Since empirical researchers cannot always derive every assumption from their theory, avoiding refutation because of those assumptions is a desirable property.

<!--statistical induction can be dangerous-->
By the same token, entire theories may escape refutation by replacing every ill-fitting statement deduced from theory with statements induced from data.
If applied to auxiliary assumptions, such a strategy of changing a theory post hoc in light of facts has been called "Lakatosian Defense" [@meehlAppraisingAmendingTheories1990].
If pushed to the limit, we arrive at a "theory" governed by the data.
Such a theory, full of empirically induced statements, is almost empty of statements that have been empirically verified.
The data used for induction cannot refute these statements, so they have never been subjected to an empirical test.
